\PassOptionsToPackage{table,xcdraw}{xcolor}

\documentclass[sigconf,review,anonymous]{acmart}
\acmConference[ESEC/FSE 2023]{The 31st ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{11 - 17 November, 2023}{San Francisco, USA}


\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{array}
\usepackage{amsmath,amsfonts}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}
\usepackage{listings}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\usepackage{balance}

\usepackage[skins]{tcolorbox}

\usepackage{xcolor,pifont}
\newcommand*\colourcheck[1]{%
	\expandafter\newcommand\csname #1check\endcsname{\textcolor{#1}{\ding{52}}}%
}
\colourcheck{blue}
\colourcheck{green}
\colourcheck{red}

\newtcolorbox{myframe}[2][]{%
  enhanced,colback=white,colframe=black,coltitle=black,
  sharp corners,
  toprule=1.0pt,
  rightrule=0.3pt,
  leftrule=0pt,
  bottomrule=0pt,
  fonttitle=\itshape\scshape\large,
  left=0pt,right=5pt,top=5pt,bottom=3pt,
  attach boxed title to top right={yshift=-0.3\baselineskip-0.4pt,xshift=-5mm},
  boxed title style={tile,size=minimal,left=0.2mm,right=0.5mm,
    colback=white,before upper=\strut},
  title=#2,#1
}

%\newcommand{\code}[1]{{\footnotesize\textsf{#1}}}

\newcommand{\tool}{\textsc{CAT}\xspace}

\newcommand{\mvpdg}{$\delta$-PDG}

\newtheorem{Definition}{Definition}
\newtheorem{Claim}{Claim}
\newtheorem{Lemma}{Lemma}
\newtheorem{Theorem}{Theorem}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newtheorem{observation}{Observation}
\newtheorem{property}{Property}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\usepackage{amsthm}
 \definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}

\newcommand{\mvpdgxy}{$\delta$-PDG$^{x,y}$}


\usepackage{tikz}
\usetikzlibrary{shapes.arrows}
\newcommand{\FancyUpArrow}{\begin{tikzpicture}[baseline=-0.3em]
		\node[single arrow,draw,rotate=90,single arrow head extend=0.1em,inner
		ysep=0.1em,transform shape,line width=0.03em,top color=green,bottom color=green!50!black] (X){};
\end{tikzpicture}}

\begin{document}

%\title[{\tool}: Deep Fault Localization with Code Coverage Representation Learning]{{\tool}: Deep Fault Localization with Code Coverage Representation Learning}

\title[Commit-level, Neural Vulnerability Detection and Assessment]{Commit-level, Neural Vulnerability Detection and Assessment}


%%%---- AUTHORS BLOCK ------

\setcopyright{none}

\settopmatter{printacmref=false, printfolios=false}

\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column


%(1) present information sorted in a way that a CNN can "see" patterns
%discriminating between faulty and non faulty statements more easily;

%(2) identify the actual crash statement to the network;

%(3) present more information to the deep neural network in the form of
%a summary of data dependences for each statement as well as source
%embedding; and

%(4) the suspiciousness of a statement is seen taking into account
%relationships to other statement, as opposed to a statement by itself”



%\input{sections/abstract}
\begin{abstract}
Software Vulnerabilities (SVs) are security flaws that are exploitable
in cyber-attacks. Delay in the detection and assessment of SVs might
cause serious consequences due to the unknown impacts on the attacked
systems. The state-of-the-art approaches have been proposed to work
directly on the committed code changes for early detection. However,
none of them could provide both commit-level vulnerability detection
and assessment at once. Moreover, the assessment approaches still
suffer low accuracy due to limited representations for code changes
and surrounding contexts.

We propose a Context-aware, Graph-based, Commit-level Vulnerability
Detection and Assessment Model, {\tool}, that evaluates a code change,
detects any vulnerability and provides the CVSS assessment grades. To
build {\tool}, we have key novel components. First, we design a novel
context-aware, graph-based, representation learning model to learn the
{\em contextualized embeddings for the code changes} that integrate
program dependencies and the surrounding contexts of code changes,
facilitating the automated vulnerability detection and
assessment. Second, {\tool} considers the mutual impact of 
learning to detect vulnerability and learning to assess each of
the vulnerability assessment types. To do so, it leverages multi-task
learning among the vulnerability detection and vulnerability
assessment tasks, improving all the tasks at the same time. Our
empirical evaluation shows that on a C vulnerability dataset, {\tool}
achieves F-score of 25.5\% and MCC of 26.9\% relatively higher than
the baselines in vulnerability assessment. In a Java dataset, {\tool}
achieves F-score of 31\% and MCC of 33.3\% relatively higher than
the baselines as well. {\tool} also improves the vulnerability
detection over the baselines from 13.4--322\% in F-score.
%16.5--25.9\% in F-score.

\end{abstract}


%mutual learning between detection and assessment

%\settopmatter{printacmref=true, printccs=true, printfolios=false}

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10011007.10011006.10011073</concept_id>
%<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Software and its engineering~Software maintenance tools}

%\keywords{Deep Learning; Automated Program Repair; Context-based Code Transformation Learning}


\maketitle

\input{sections/intro_1}

\input{sections/motiv}

\input{sections/key-ideas}

\input{sections/overview}

\input{sections/multiversion}

\input{sections/embedding}

\input{sections/classification}


\input{sections/experiment}

%\input{sections/discussions}

\input{sections/threats}

\input{sections/relatedstudy}

\input{sections/conclusion}

\subsection*{Data Availability}

Our data and code are available at~\cite{cat-website}.

\newpage

\balance

%\bibliographystyle{plain}
%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{ACM-Reference-Format}

\bibliography{References,icse23}

\end{document}
